---
title: "Power of R"
author: "Team CDMA"
date: '2022-06-30'
output: powerpoint_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Demonstrated through three data analytics projects

Load Libraries
```{r message=FALSE, warning=FALSE, echo=TRUE}
library(tidyverse)
library(knitr)
library(igraph)
library(networkD3)
library(visNetwork)
library(tidytext) #install.packages("tidytext")
library(wordcloud) #install.packages("wordcloud")
library(ggtext)
library(ggalt)
library(ggthemes)
library(ggpubr)
```

## 1.Sentiment Analysis through Word Cloud

Data Source: [Indian Budget Portal](https://www.indiabudget.gov.in/)

Load data
```{r warning=FALSE,message=FALSE}
dat <- read.table('budget.txt', header = FALSE, fill = TRUE)
```

reshape the .txt data frame into one column
```{r echo=TRUE}
tidy_dat <- dat %>% 
  pivot_longer(everything(), values_to = 'word', names_to = NULL)
```
Tokenize
```{r echo=TRUE}
tokens <- tidy_dat %>% 
  unnest_tokens(word, word) %>% 
  count(word, sort = TRUE) 
```
##
Load default stop words
```{r echo=TRUE}
data("stop_words")
```

Remove stop words using dplyr::anti_join
```{r echo=TRUE}
tokens_clean <- tokens %>%
  anti_join(stop_words, by='word') %>% 
  # remove numbers
  filter(!str_detect(word, "^[0-9]"))
```
Remove additional words seen in first round
```{r echo=TRUE}
uni_sw <- data.frame(word = c("cent", "pm", "crore", 
                              "lakh", "set",
                              "level", "sir"))

tokens_clean <- tokens_clean %>% 
  anti_join(uni_sw, by = "word")
```
##
Plot

```{r message=FALSE, warning=FALSE}
pal <- RColorBrewer::brewer.pal(8,"Dark2")

# plot the 50 most common words
tokens_clean %>% 
  with(wordcloud(word, 
                 n, 
                 random.order = FALSE, 
                 max.words = 75, 
                 colors=pal,
                 scale=c(2.5, .5)))
```

## 2.Customisation available in R visualisation

Customisation at micro level, e.g. adding icons, country flags, etc. in Axes of Plots generated.

Data Set used- 120 Years of Olympics
Source: [Kaggle](https://www.kaggle.com/datasets/heesoo37/120-years-of-olympic-history-athletes-and-results)

## Output plot

```{r message=FALSE, warning=FALSE}
olympics <- read_csv("athlete_events.csv")
NOC_dat <- read_csv('noc_regions.csv')
NOC_dat <- NOC_dat[,-3]
```


```{r out.width="100%"}
olymp4 <- olympics %>%
  filter(!is.na(Medal)) %>%
  left_join(NOC_dat, by = 'NOC') %>%
  group_by(region, Season, Medal) %>%
  summarise(count = n_distinct(Event), .groups = 'drop') %>%
  group_by(region, Season) %>%
  mutate(tot = sum(count)) %>%
  group_by(Season) %>%
  slice_max(tot, n = 45) %>%
  ungroup() %>%
  mutate(Medal = factor(Medal, 
                        levels = c('Bronze', 'Silver', 'Gold'), 
                        ordered = TRUE),
         region = reorder_within(region, count, Season))

olymp4 %>%
  filter(Season == 'Summer') %>%
  mutate(l_1 = paste0(gsub('___.*$', '', region), ' ',
                      '<img src = senojflags/', 
                      gsub('___.*$', '', region), '-Flag.png height = "20" />' 
  )) -> olymp4_r2

olymp4_r2 %>%  
  ggplot(aes(x = region, y = count, fill = Medal, label = count)) +
  geom_col(position = 'stack') +
  geom_text(size = 4, position = position_stack(vjust = 0.5)) +
  scale_fill_manual(values=c("#cd7f32","gray70","#c9b037")) +
  scale_x_discrete(labels = rev(unique(olymp4_r2$l_1))) +
  coord_flip() +
  theme(legend.position = 'top',
        axis.text.y = element_markdown(size = 17)) +
  labs(y = 'Medals', fill = '', x = '', 
       title = "Top-10 Countries by Medals won",
       subtitle = "120 years of Summer Olympics")+
  theme(plot.background = element_rect(color = "black", size = 1.5))
```

## 3. Network Analysis and Visualisation

Data Set - Export Schemes data sample

A beneficiary is entitled to get only one Import/Export Code.  However network analysis revealed that a single beneficiary was enrolled using different attributes such as mobile number, email, PAN, bank account number, etc. and obtained multiple IECs.

Data points analysed

- Unique IE Code
- Other Identification attributes, such as
  + Mobile number
  + E-mail
  + PAN Number
  
## 

Code Explanation: Steps-

1. Load data.  
2. Convert all attributes to tidy format, using `tidyr::pivot_longer()`
3. Convert it to graph object, using `igraph` library.
4. Add attributes(color and shape) for each node
5. Plot interactive plot using `visNetwork` library.


```{r message=FALSE, warning=FALSE}
IEC_data <- read_csv('sample_data.csv')
```

## Preview the data
```{r}
knitr::kable(IEC_data)
```

## Performing network analysis

```{r}
#Change in long format
IEC_data %>% 
  mutate(across(everything(), as.character)) %>% 
  pivot_longer(!IE_code, 
               names_to = 'Attribute',
               values_to = 'Attrib_value') %>% 
  relocate(Attribute, .after = 3) -> long_data

# graph object
g <- graph_from_data_frame(long_data)

# Long format all columns
long_data2 <- IEC_data %>% 
  mutate(across(everything(), as.character)) %>% 
  pivot_longer(everything(), 
               names_to = 'Attribute',
               values_to = 'Attrib_value') %>% 
  distinct()

# Re-order using joins
V(g)$att_type <- V(g)$name %>% 
  as.data.frame() %>% 
  set_names('name') %>% 
  inner_join(long_data2, by = c("name" = "Attrib_value")) %>% 
  pull(Attribute)

V(g)$color <- c('steel blue', 'orange')[1 + (V(g)$att_type == 'IE_code')]

V(g)$shape <- c("square", "circle")[(V(g)$att_type == 'IE_code')+1]

```

```{r graplot, fig.show='hold'}
plot(g)
```


```{r}
output <- g %>% 
  components() %>% 
  pluck(membership) %>% 
  stack() %>% 
  set_names(c('Group_id', 'IE_code')) %>% 
  right_join(IEC_data %>% 
               mutate(IE_code = as.factor(IE_code)),
             by = "IE_code")

knitr::kable(output)
```


## Features of R used -

+ Level of customisation available
+ Better readable and concise code
+ Interactive visualisations
+ Tidy data concepts laid down by Hadley Wickham, widely used across many programming languages such as pandas in python, tableau, etc.
+ Functional programming aspects of `dplyr::across` - a powerful function to perform large number of analysis in one single line of code. 
+ Network Analysis, Word Cloud, etc. otherwise not possible in many licensed softwares such as Tableau and Power BI, without knowledge of R/Python.


