---
title: "Power of Visualisations in R"
author: "Team CDMA"
date: '2022-06-30'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Power of Visualisations in R

Demonstrated through three projects

### Load Libraries
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(knitr)
library(igraph)
library(networkD3)
library(visNetwork)
library(tidytext) #install.packages("tidytext")
library(wordcloud) #install.packages("wordcloud")
library(ggtext)
library(ggalt)
library(ggthemes)
library(ggpubr)
```


## 1. Network Analysis and Visualisation

Explain Data

- Unique IE Code
- Other Identification attributes, such as
  + Mobile number
  + E-mail
  + PAN Number
  
  
Code Explanation: Steps-

1. Load data.  
2. Convert all attributes to tidy format, using `tidyr::pivot_longer()`
3. Convert it to graph object, using `igraph` library.
4. Add attributes(color and shape) for each node
5. Plot interactive plot using `visNetwork` library.


```{r}
IEC_data <- read_csv('sample_data.csv')
```

Preview the data
```{r}
knitr::kable(IEC_data)
```

Performing network analysis

```{r}
#Change in long format
IEC_data %>% 
  mutate(across(everything(), as.character)) %>% 
  pivot_longer(!IE_code, 
               names_to = 'Attribute',
               values_to = 'Attrib_value') %>% 
  relocate(Attribute, .after = 3) -> long_data

# graph object
g <- graph_from_data_frame(long_data)

# Long format all columns
long_data2 <- IEC_data %>% 
  mutate(across(everything(), as.character)) %>% 
  pivot_longer(everything(), 
               names_to = 'Attribute',
               values_to = 'Attrib_value') %>% 
  distinct()

# Re-order using joins
V(g)$att_type <- V(g)$name %>% 
  as.data.frame() %>% 
  set_names('name') %>% 
  inner_join(long_data2, by = c("name" = "Attrib_value")) %>% 
  pull(Attribute)

V(g)$color <- c('steel blue', 'orange')[1 + (V(g)$att_type == 'IE_code')]

V(g)$shape <- c("square", "circle")[(V(g)$att_type == 'IE_code')+1]

```

Plot the object
```{r echo=FALSE,fig.align='center', fig.width=7, fig.cap="Network Diagram of Duplicate Importers Exporters detected through network analysis"}
visIgraph(g)
```

Features of R used -

+ Power of interactive visualisations
+ Tidy data concepts laid down by Hadley Wickham, widely used across many programming languages such as pandas in python, tableau, etc.
+ Functional programming aspects of `dplyr::across` which is a powerful function to perform large number of analysis in one single line of code.  E.g. all columns mutated as character type using singe command.
+ Network Analysis, otherwise not possible in many licensed softwares such as Tableau and Power BI, without knowledge of R/Python.

## Sentiment Analysis through Word Cloud

```{r}
dat <- read.table('budget.txt', header = FALSE, fill = TRUE)

# reshape the .txt data frame into one column
tidy_dat <- tidyr::gather(dat, key, word) %>% select(word)

# tokenize
tokens <- tidy_dat %>% 
  unnest_tokens(word, word) %>% 
  count(word, sort = TRUE) %>% 
  ungroup()

data("stop_words")

tokens_clean <- tokens %>%
  anti_join(stop_words)

# remove numbers
nums <- tokens_clean %>% filter(str_detect(word, "^[0-9]")) %>% select(word) %>% unique()

tokens_clean <- tokens_clean %>% 
  anti_join(nums, by = "word")

# remove unique stop words that snuck in there
uni_sw <- data.frame(word = c("cent", 
                              "pm", 
                              "crore", 
                              "lakh",
                              "set",
                              "level",
                              "sir"))

tokens_clean <- tokens_clean %>% 
  anti_join(uni_sw, by = "word")

pal <- brewer.pal(8,"Dark2")

# plot the 50 most common words
tokens_clean %>% 
  with(wordcloud(word, n, 
                 random.order = FALSE, 
                 max.words = 75, 
                 colors=pal,
                 scale=c(2.5, .5)))
```


## Customisation and Interactivity available in R visualisation

```{r out.width="100%"}
olympics <- read_csv("athlete_events.csv")
NOC_dat <- read_csv('noc_regions.csv')
NOC_dat <- NOC_dat[,-3]

olymp4 <- olympics %>%
  filter(!is.na(Medal)) %>%
  left_join(NOC_dat, by = 'NOC') %>%
  group_by(region, Season, Medal) %>%
  summarise(count = n_distinct(Event), .groups = 'drop') %>%
  group_by(region, Season) %>%
  mutate(tot = sum(count)) %>%
  group_by(Season) %>%
  slice_max(tot, n = 45) %>%
  ungroup() %>%
  mutate(Medal = factor(Medal, levels = c('Bronze', 'Silver', 'Gold'), ordered = TRUE),
         region = reorder_within(region, count, Season))

olymp4 %>%
      filter(Season == 'Summer') %>%
      mutate(l_1 = paste0(gsub('___.*$', '', region), ' ',
                          '<img src = senojflags/', 
                        gsub('___.*$', '', region), '-Flag.png height = "20" />' 
                        )) -> olymp4_r2
    
    olymp4_r2 %>%  
      ggplot(aes(x = region, y = count, fill = Medal, label = count)) +
      geom_col(position = 'stack') +
      geom_text(size = 4, position = position_stack(vjust = 0.5)) +
      scale_fill_manual(values=c("#cd7f32","gray70","#c9b037")) +
      scale_x_discrete(labels = rev(unique(olymp4_r2$l_1))) +
      coord_flip() +
      theme(legend.position = 'top',
            axis.text.y = element_markdown(size = 17)) +
      labs(y = 'Medals', fill = '', x = '', 
           title = "Top-10 Countries by Medals won",
           subtitle = "120 years of Summer Olympics")+
      theme(plot.background = element_rect(color = "black", size = 1.5))
```



